Beta Diversity through Time and Space

### 2020-09-09 analyses/beta_diversity_v2.Rmd
make beta-div analysis more solid

### Tabulate webs
S	= beta_S, the dissimilarity in species composition
OS = beta_OS, the dissimilarity (component) explained by "rewiring" among shared species
WN = beta_WN, the dissimilarity between the two networks
ST = beta_ST, the dissimilarity (component) explained by difference in species community composition 
```{r message=FALSE}
net2010 <- filter(net, year == 2010) %>%
  unite(site.date, c(site, date), sep = "_") %>%
  group_by(site.date, bb.sp, plant.sp) %>%
  summarize(freq = n()) %>% 
  dplyr::select(higher = bb.sp, lower = plant.sp, webID = site.date, freq) %>% # rename columns to match bipartite's expectations
  data.frame() %>% # convert to data frame
  frame2webs()

net2011 <- filter(net, year == 2011) %>%
  unite(site.date, c(site, date), sep = "_") %>%
  group_by(site.date, bb.sp, plant.sp) %>%
  summarize(freq = n()) %>% 
  dplyr::select(higher = bb.sp, lower = plant.sp, webID = site.date, freq) %>% # rename columns to match bipartite's expectations
  data.frame() %>% # convert to data frame
  frame2webs()

net2012 <- filter(net, year == 2012) %>%
  unite(site.date, c(site, date), sep = "_") %>%
  group_by(site.date, bb.sp, plant.sp) %>%
  summarize(freq = n()) %>% 
  dplyr::select(higher = bb.sp, lower = plant.sp, webID = site.date, freq) %>% # rename columns to match bipartite's expectations
  data.frame() %>% # convert to data frame
  frame2webs()

array_site.date.2010 <- webs2array(net2010) # convert to array of webs
array_site.date.2011 <- webs2array(net2011) # convert to array of webs
array_site.date.2012 <- webs2array(net2012) # convert to array of webs

beta_site.date.2010 <- betalinkr_multi(array_site.date.2010, 
                                       partition.st = TRUE, 
                                       partition.rr = TRUE) %>%
  as_tibble() %>%
  separate(i, into = c("site1", "year1", "yday1"), sep = "_") %>%
  separate(j, into = c("site2", "year2", "yday2"), sep = "_") %>%
  left_join(site_data, by = c("site1" = "site"))%>%
  dplyr::select(site1, year1, yday1, site2, year2, yday2, S, OS, WN, ST, 
                ST.l, ST.h, ST.lh, WN.repl, OS.repl, WN.rich, OS.rich, 
                elev1 = elev.mean, man1 = management, lon1 = lon, lat1 = lat) %>%
  left_join(site_data, by = c("site2" = "site")) %>%
  dplyr::select(site1, year1, yday1, site2, year2, yday2, S, OS, WN, ST, 
                ST.l, ST.h, ST.lh, WN.repl, OS.repl, WN.rich, OS.rich, 
                elev1, elev2 = elev.mean, man1, man2 = management, lon1, lat1, lon2 = lon, lat2 = lat) %>%
  mutate(site1 = factor(site1),
         site2 = factor(site2),
         year1 = factor(year1),
         year2 = factor(year2),
         yday1 = as.numeric(yday1),
         yday2 = as.numeric(yday2),
         elev.diff = abs(elev1 - elev2),
         mean.elev = (elev1 + elev2)/2,
         yday.diff = abs(yday1 - yday2),
         man.diff = case_when(
           man1 == man2 ~ FALSE,
           man1 != man2 ~ TRUE
         )) %>%
  gather(metric, value, -c(site1, year1, yday1, site2, year2, yday2,
                           elev1, elev2, elev.diff, yday.diff, 
                           man1, man2, man.diff, mean.elev, 
                           lon1, lat1, lon2, lat2)) %>%
  mutate(metric.class = case_when(
    metric %in% c("WN", "ST", "OS", "S") ~ "aggregate",
    metric %in% c("WN.repl", "WN.rich") ~ "WN.partition",
    metric %in% c("ST.h", "ST.l", "ST.lh") ~ "ST.partition",
    metric %in% c("OS.repl", "OS.rich") ~ "OS.partition"
  ))

beta_site.date.2011 <- betalinkr_multi(array_site.date.2011, 
                                       partition.st = TRUE, 
                                       partition.rr = TRUE) %>%
  as_tibble() %>%
  separate(i, into = c("site1", "year1", "yday1"), sep = "_") %>%
  separate(j, into = c("site2", "year2", "yday2"), sep = "_") %>%
  left_join(site_data, by = c("site1" = "site"))%>%
  dplyr::select(site1, year1, yday1, site2, year2, yday2, S, OS, WN, ST, 
                ST.l, ST.h, ST.lh, WN.repl, OS.repl, WN.rich, OS.rich, 
                elev1 = elev.mean, man1 = management, lon1 = lon, lat1 = lat) %>%
  left_join(site_data, by = c("site2" = "site")) %>%
  dplyr::select(site1, year1, yday1, site2, year2, yday2, S, OS, WN, ST, 
                ST.l, ST.h, ST.lh, WN.repl, OS.repl, WN.rich, OS.rich, 
                elev1, elev2 = elev.mean, man1, man2 = management, lon1, lat1, lon2 = lon, lat2 = lat) %>%
  mutate(site1 = factor(site1),
         site2 = factor(site2),
         year1 = factor(year1),
         year2 = factor(year2),
         yday1 = as.numeric(yday1),
         yday2 = as.numeric(yday2),
         elev.diff = abs(elev1 - elev2),
         mean.elev = (elev1 + elev2)/2,
         yday.diff = abs(yday1 - yday2),
         man.diff = case_when(
           man1 == man2 ~ FALSE,
           man1 != man2 ~ TRUE
         )) %>%
  gather(metric, value, -c(site1, year1, yday1, site2, year2, yday2,
                           elev1, elev2, elev.diff, yday.diff, 
                           man1, man2, man.diff, mean.elev, 
                           lon1, lat1, lon2, lat2)) %>%
  mutate(metric.class = case_when(
    metric %in% c("WN", "ST", "OS", "S") ~ "aggregate",
    metric %in% c("WN.repl", "WN.rich") ~ "WN.partition",
    metric %in% c("ST.h", "ST.l", "ST.lh") ~ "ST.partition",
    metric %in% c("OS.repl", "OS.rich") ~ "OS.partition"
  ))

beta_site.date.2012 <- betalinkr_multi(array_site.date.2012, 
                                       partition.st = TRUE, 
                                       partition.rr = TRUE) %>%
  as_tibble() %>%
  separate(i, into = c("site1", "year1", "yday1"), sep = "_") %>%
  separate(j, into = c("site2", "year2", "yday2"), sep = "_") %>%
  left_join(site_data, by = c("site1" = "site"))%>%
  dplyr::select(site1, year1, yday1, site2, year2, yday2, S, OS, WN, ST, 
                ST.l, ST.h, ST.lh, WN.repl, OS.repl, WN.rich, OS.rich, 
                elev1 = elev.mean, man1 = management, lon1 = lon, lat1 = lat) %>%
  left_join(site_data, by = c("site2" = "site")) %>%
  dplyr::select(site1, year1, yday1, site2, year2, yday2, S, OS, WN, ST, 
                ST.l, ST.h, ST.lh, WN.repl, OS.repl, WN.rich, OS.rich, 
                elev1, elev2 = elev.mean, man1, man2 = management, lon1, lat1, lon2 = lon, lat2 = lat) %>%
  mutate(site1 = factor(site1),
         site2 = factor(site2),
         year1 = factor(year1),
         year2 = factor(year2),
         yday1 = as.numeric(yday1),
         yday2 = as.numeric(yday2),
         elev.diff = abs(elev1 - elev2),
         mean.elev = (elev1 + elev2)/2,
         yday.diff = abs(yday1 - yday2),
         man.diff = case_when(
           man1 == man2 ~ FALSE,
           man1 != man2 ~ TRUE
         )) %>%
  gather(metric, value, -c(site1, year1, yday1, site2, year2, yday2,
                           elev1, elev2, elev.diff, yday.diff, 
                           man1, man2, man.diff, mean.elev, 
                           lon1, lat1, lon2, lat2)) %>%
  mutate(metric.class = case_when(
    metric %in% c("WN", "ST", "OS", "S") ~ "aggregate",
    metric %in% c("WN.repl", "WN.rich") ~ "WN.partition",
    metric %in% c("ST.h", "ST.l", "ST.lh") ~ "ST.partition",
    metric %in% c("OS.repl", "OS.rich") ~ "OS.partition"
  ))

beta_site.date <- bind_rows(beta_site.date.2010, beta_site.date.2011, beta_site.date.2012)
beta_site.date_gdm.prep <- beta_site.date %>%
  filter(metric == "WN")

write_csv(beta_site.date, "../analyses/output/beta_site.date.csv")
beta_site.date <- read_csv("../analyses/output/beta_site.date.csv") %>%
  mutate(year1 = factor(year1),
         year2 = factor(year2),
         metric = factor(metric))
```

### Plot results. There's nothing a Mantel test can tell me that I don't already know from the combination of plotting and GDM analysis.
```{r}
### Elevation diff
ggplot(filter(beta_site.date, year1 == year2,
                metric != "S" & 
                metric.class != "OS.partition"), 
       aes(elev.diff, value, color = metric)) +
  geom_point(alpha = 0.15, size = 0.5) +
  geom_smooth() +
  facet_grid(metric.class ~ year1) +
  theme_abyss()

### Time diff
ggplot(filter(beta_site.date, year1 == year2,
                metric != "S" & 
                metric.class != "OS.partition"), 
       aes(yday.diff, value, color = metric)) +
  geom_point(alpha = 0.15, size = 0.5) +
  geom_smooth() +
  facet_grid(metric.class ~ year1) +
  theme_abyss()

### Elevation diff within 1 wk time diff
ggplot(filter(beta_site.date, year1 == year2,
                metric != "S" & 
                metric.class != "OS.partition" &
                yday.diff <= 7), 
       aes(elev.diff, value, color = metric)) +
  geom_point(alpha = 0.15, size = 0.5) +
  geom_smooth() +
  facet_wrap(~metric.class) +
  theme_light()

ggplot(filter(beta_site.date, year1 == year2,
                metric != "S" & 
                metric.class != "OS.partition" &
                yday.diff <= 7), 
       aes(elev.diff, value, color = metric)) +
  geom_point(alpha = 0.15, size = 0.5) +
  geom_smooth() +
  facet_grid(metric.class ~ year1) +
  theme_abyss()

### Time diff within 250 m elev diff
ggplot(filter(beta_site.date, year1 == year2,
                metric != "S" & 
                metric.class != "OS.partition" &
                elev.diff <= 7), 
       aes(yday.diff, value, color = metric)) +
  geom_point(alpha = 0.15, size = 0.5) +
  geom_smooth() +
  facet_wrap(~metric.class) +
  theme_light()

ggplot(filter(beta_site.date, year1 == year2,
                metric != "S" & 
                metric.class != "OS.partition" &
                elev.diff <= 7), 
       aes(yday.diff, value, color = metric)) +
  geom_point(alpha = 0.15, size = 0.5) +
  geom_smooth() +
  facet_grid(metric.class ~ year1) +
  theme_abyss()

### 2D ElevationDiff*TimeDiff
gam_betadiv <- bamV(value ~ te(elev.diff, yday.diff, 
                               bs = c("te", "te"),
                               k = c(10, 10)),
                    family = "quasibinomial",
                    data = filter(beta_site.date, year1 == year2 &
                                    metric == "WN"),
                    method = "REML")

gam_betadiv <- bam(value ~ 
                     s(year1, bs = "re") +
                     te(yday.diff, elev.diff, k = c(10, 10)),
                   data = filter(beta_site.date, year1 == year2 &
                                   metric == "WN.rich"),
                   family = "quasibinomial",
                   discrete = TRUE,
                   method = "fREML") %>% getViz()

@@

### GDM analysis. I don't think p-values would add anything to the interpretation I get from the plotted uncertainty, so it's okay that I can't get gdm.varImp() to work.
```{r}
### 2010
sitepair_2010.WN <- beta_site.date %>%
  ungroup() %>%
  filter(year1 == year2 & year1 == 2010) %>%
  filter(metric == "WN") %>%
  mutate(weights = rep(1, n())) %>%
  dplyr::select(distance = value, weights,
         s1.xCoord = lon1, s1.yCoord = lat1, 
         s2.xCoord = lon2, s2.yCoord = lat2, 
         s1.elev = elev1, s1.yday = yday1,
         s2.elev = elev2, s2.yday = yday2) %>%
  data.frame()

@@

### 2011
sitepair_2011.WN <- beta_site.date %>%
  ungroup() %>%
  filter(year1 == year2 & year1 == 2011) %>%
  filter(metric == "WN") %>%
  mutate(weights = rep(1, n())) %>%
  dplyr::select(distance = value, weights,
         s1.xCoord = lon1, s1.yCoord = lat1, 
         s2.xCoord = lon2, s2.yCoord = lat2, 
         s1.elev = elev1, s1.yday = yday1,
         s2.elev = elev2, s2.yday = yday2) %>%
  data.frame()

@@

### 2012
sitepair_2012.WN <- beta_site.date %>%
  ungroup() %>%
  filter(year1 == year2 & year1 == 2012) %>%
  filter(metric == "WN") %>%
  mutate(weights = rep(1, n())) %>%
  dplyr::select(distance = value, weights,
         s1.xCoord = lon1, s1.yCoord = lat1, 
         s2.xCoord = lon2, s2.yCoord = lat2, 
         s1.elev = elev1, s1.yday = yday1,
         s2.elev = elev2, s2.yday = yday2) %>%
  data.frame()

@@

### Let's look at per-transect floral survey beta-diversity
```{r}
### 2012
survey_bioData.2012 <- survey %>%
  mutate(year = year(date),
         yday = yday(date)) %>%
  filter(flower.cover > 0 & year == "2012") %>%
  mutate(plant.sp = str_replace_all(plant.sp, " ", "_")) %>%
  group_by(site, yday, plant.sp) %>%
  summarize(cover = sum(flower.cover)) %>%
  spread(plant.sp, cover) %>%
  replace(is.na(.), 0) %>%
  arrange(site, yday) %>%
  unite(site.day, site, yday, sep = "_")

@@

survey_sitepair.2012 <- formatsitepair(survey_bioData.2012, bioFormat = 1, siteColumn = "site.day", dist = "jaccard",
                              XColumn = "lon", YColumn = "lat", predData = survey_predData.2012)

@@

### 2011
survey_bioData.2011 <- survey %>%
  mutate(year = year(date),
         yday = yday(date)) %>%
  filter(flower.cover > 0 & year == "2011") %>%
  mutate(plant.sp = str_replace_all(plant.sp, " ", "_")) %>%
  group_by(site, yday, plant.sp) %>%
  summarize(cover = sum(flower.cover)) %>%
  spread(plant.sp, cover) %>%
  replace(is.na(.), 0) %>%
  arrange(site, yday) %>%
  unite(site.day, site, yday, sep = "_")

predData.2011 <- survey %>%
  mutate(year = year(date),
         yday = yday(date)) %>%
  filter(flower.cover > 0 & year == "2011") %>%
  select(site, yday) %>%
  left_join(site_data) %>%
  ungroup() %>%
  dplyr::select(site, elev.mean, lat, lon, yday) %>%
  unique() %>%
  arrange(site, yday) %>%
  unite(site.day, site, yday, sep = "_", remove = "FALSE") %>%
  select(-site)

survey_sitepair.2011 <- formatsitepair(survey_bioData.2011, bioFormat = 1, siteColumn = "site.day", dist = "jaccard",
                              XColumn = "lon", YColumn = "lat", predData = predData.2011)

@@

### 2010
survey_bioData.2010 <- survey %>%
  mutate(year = year(date),
         yday = yday(date)) %>%
  filter(flower.cover > 0 & year == "2010") %>%
  mutate(plant.sp = str_replace_all(plant.sp, " ", "_")) %>%
  group_by(site, yday, plant.sp) %>%
  summarize(cover = sum(flower.cover)) %>%
  spread(plant.sp, cover) %>%
  replace(is.na(.), 0) %>%
  arrange(site, yday) %>%
  unite(site.day, site, yday, sep = "_")

@@

summary(gdm_bb.2012)
plot(gdm_bb.2012)
plotUncertainty(bb_sitepair.2012, sampleSites = 0.7, bsIters = 50, geo  = TRUE)
```

>>>>

### Tabulate webs
S	= beta_S, the dissimilarity in species composition
OS = beta_OS, the dissimilarity (component) explained by "rewiring" among shared species
WN = beta_WN, the dissimilarity between the two networks
ST = beta_ST, the dissimilarity (component) explained by difference in species community composition 
```{r message=FALSE}
# Create webs
net2010 <- filter(net, year == 2010) %>%
  unite(site.date, c(site, date), sep = "_") %>%
  group_by(site.date, bb.sp, plant.sp) %>%
  summarize(freq = n()) %>%
  group_by(site.date) %>%
  mutate(bb.sp.count = length(unique(bb.sp)),
         plant.sp.count = length(unique(plant.sp))) %>%
  ungroup() %>%
  filter(bb.sp.count > 1 & plant.sp.count > 1) %>% # the betalinkr function fails if you feed it webs with only 1 species in either (or perhaps both) of the levels; this is probably for good reason.
  dplyr::select(higher = bb.sp, lower = plant.sp, webID = site.date, freq) %>% # rename columns to match bipartite's expectations
  data.frame() %>% # convert to data frame
  frame2webs(type.out = "array")

net2011 <- filter(net, year == 2011) %>%
  unite(site.date, c(site, date), sep = "_") %>%
  group_by(site.date, bb.sp, plant.sp) %>%
  summarize(freq = n()) %>%
  group_by(site.date) %>%
  mutate(bb.sp.count = length(unique(bb.sp)),
         plant.sp.count = length(unique(plant.sp))) %>%
  ungroup() %>%
  filter(bb.sp.count > 1 & plant.sp.count > 1) %>% 
  dplyr::select(higher = bb.sp, lower = plant.sp, webID = site.date, freq) %>% # rename columns to match bipartite's expectations
  data.frame() %>% # convert to data frame
  frame2webs(type.out = "array")

net2012 <- filter(net, year == 2012) %>%
  unite(site.date, c(site, date), sep = "_") %>%
  group_by(site.date, bb.sp, plant.sp) %>%
  summarize(freq = n()) %>%
  group_by(site.date) %>%
  mutate(bb.sp.count = length(unique(bb.sp)),
         plant.sp.count = length(unique(plant.sp))) %>%
  ungroup() %>%
  filter(bb.sp.count > 1 & plant.sp.count > 1) %>% 
  dplyr::select(higher = bb.sp, lower = plant.sp, webID = site.date, freq) %>% # rename columns to match bipartite's expectations
  data.frame() %>% # convert to data frame
  frame2webs(type.out = "array")

# Calculate beta-diversity
beta_site.date.2010 <- betalinkr_multi(net2010, 
                                       partition.st = TRUE, 
                                       partition.rr = TRUE,
                                       binary = TRUE,
                                       index = "jaccard") %>%
  as_tibble()

beta_site.date.2011 <- betalinkr_multi(net2011, 
                                       partition.st = TRUE, 
                                       partition.rr = TRUE,
                                       binary = TRUE,
                                       index = "jaccard") %>%
  as_tibble()

beta_site.date.2012 <- betalinkr_multi(net2012, 
                                       partition.st = TRUE, 
                                       partition.rr = TRUE,
                                       binary = TRUE,
                                       index = "jaccard") %>%
  as_tibble()

# Collate results into a single tibble
beta_site.date <- bind_rows(beta_site.date.2010, beta_site.date.2011, beta_site.date.2012)

# Save to file to avoid redoing that long step
write_csv(beta_site.date, "./output/beta_site.date.csv")
#beta_site.date <- read_csv("./output/beta_site.date.csv")

# Add site data
beta_mit_data <- beta_site.date %>%
  separate(i, into = c("site1", "date1"), sep = "_") %>%
  separate(j, into = c("site2", "date2"), sep = "_") %>%
  mutate(date1 = ymd(date1),
         date2 = ymd(date2),
         year1 = factor(year(date1)),
         year2 = factor(year(date2)),
         yday1 = yday(date1),
         yday2 = yday(date2)) %>%
  left_join(site_data, by = c("site1" = "site")) %>%
  dplyr::select(site1, year1, yday1, site2, year2, yday2, S, OS, WN, ST, 
                ST.l, ST.h, ST.lh, WN.repl, OS.repl, WN.rich, OS.rich, 
                elev1 = elev.mean, man1 = management, lon1 = lon, lat1 = lat) %>%
  left_join(site_data, by = c("site2" = "site")) %>%
  dplyr::select(site1, year1, yday1, site2, year2, yday2, S, OS, WN, ST, 
                ST.l, ST.h, ST.lh, WN.repl, OS.repl, WN.rich, OS.rich, 
                elev1, elev2 = elev.mean, man1, man2 = management, lon1, lat1, lon2 = lon, lat2 = lat) %>%
  mutate(site1 = factor(site1),
         site2 = factor(site2),
         year1 = factor(year1),
         year2 = factor(year2),
         yday1 = as.numeric(yday1),
         yday2 = as.numeric(yday2),
         elev.diff = abs(elev1 - elev2),
         mean.elev = (elev1 + elev2)/2,
         yday.diff = abs(yday1 - yday2),
         man.diff = case_when(
           man1 == man2 ~ FALSE,
           man1 != man2 ~ TRUE
         )) %>%
  gather(metric, value, -c(site1, year1, yday1, site2, year2, yday2,
                           elev1, elev2, elev.diff, yday.diff, 
                           man1, man2, man.diff, mean.elev, 
                           lon1, lat1, lon2, lat2)) %>%
  mutate(metric.class = case_when(
    metric %in% c("WN", "ST", "OS", "S") ~ "aggregate",
    metric %in% c("WN.repl", "WN.rich") ~ "WN.partition",
    metric %in% c("ST.h", "ST.l", "ST.lh") ~ "ST.partition",
    metric %in% c("OS.repl", "OS.rich") ~ "OS.partition"
  ))
```

### Plot results. There's nothing a Mantel test can tell me that I don't already know from the combination of plotting and GDM analysis.
```{r}
### Elevation diff
ggplot(filter(beta_mit_data, year1 == year2 &
                site1 != site2 &
                metric != "S" & 
                metric.class != "OS.partition"), 
       aes(elev.diff, value, color = metric)) +
  geom_point(alpha = 0.25, pch = 16) +
  geom_smooth() +
  facet_grid(metric.class ~ year1) +
  theme_abyss()

### Time diff
ggplot(filter(beta_mit_data, year1 == year2 &
                site1 != site2 &
                metric != "S" & 
                metric.class != "OS.partition"), 
       aes(yday.diff, value, color = metric)) +
  geom_point(alpha = 0.25, pch = 16) +
  geom_smooth() +
  facet_grid(metric.class ~ year1) +
  theme_abyss()

### Elevation diff within 1 wk time diff
ggplot(filter(beta_mit_data, year1 == year2 &
                site1 != site2 &
                metric != "S" & 
                metric.class != "OS.partition" &
                yday.diff <= 7), 
       aes(elev.diff, value, color = metric)) +
  geom_point(alpha = 0.15, pch = 16, size = 1) +
  geom_smooth() +
  facet_wrap(~metric.class) +
  theme_light()

### Time diff within 250 m elev diff
ggplot(filter(beta_mit_data, year1 == year2 &
                site1 != site2 &
                metric != "S" & 
                metric.class != "OS.partition" &
                elev.diff <= 250), 
       aes(yday.diff, value, color = metric)) +
  geom_point(alpha = 0.15, pch = 16, size = 1) +
  geom_smooth() +
  facet_wrap(~metric.class) +
  theme_light()

### 2D ElevationDiff*TimeDiff
gam_betadiv <- bamV(value ~ te(elev.diff, yday.diff, 
                               bs = c("te", "te"),
                               k = c(10, 10)),
                    family = "quasibinomial",
                    data = filter(beta_mit_data, year1 == year2 &
                                    metric == "WN"),
                    method = "REML")

gam_betadiv <- bam(value ~ 
                     s(year1, bs = "re") +
                     te(yday.diff, elev.diff, k = c(10, 10)),
                   data = filter(beta_mit_data, year1 == year2 &
                                   metric == "WN.rich"),
                   family = "quasibinomial",
                   discrete = TRUE,
                   method = "fREML") %>% getViz()

@@

### GDM analysis.
```{r}
### 2010
sitepair_2010.WN <- beta_mit_data %>%
  ungroup() %>%
  filter(year1 == year2 & year1 == 2010 & site1 != site2) %>% # I don't think we want to compare samples through within sites, since this introduces a new form of non-independence.
  filter(metric == "WN") %>%
  mutate(weights = rep(1, n())) %>%
  dplyr::select(distance = value, weights,
         s1.xCoord = lon1, s1.yCoord = lat1, 
         s2.xCoord = lon2, s2.yCoord = lat2, 
         s1.elev = elev1, s1.yday = yday1,
         s2.elev = elev2, s2.yday = yday2) %>%
  data.frame()

@@

### 2011
sitepair_2011.WN <- beta_mit_data %>%
  ungroup() %>%
  filter(year1 == year2 & year1 == 2011 & site1 != site2) %>%
  filter(metric == "WN") %>%
  mutate(weights = rep(1, n())) %>%
  dplyr::select(distance = value, weights,
         s1.xCoord = lon1, s1.yCoord = lat1, 
         s2.xCoord = lon2, s2.yCoord = lat2, 
         s1.elev = elev1, s1.yday = yday1,
         s2.elev = elev2, s2.yday = yday2) %>%
  data.frame()

@@

### 2012
sitepair_2012.WN <- beta_mit_data %>%
  ungroup() %>%
  filter(year1 == year2 & year1 == 2012 & site1 != site2) %>%
  filter(metric == "WN") %>%
  mutate(weights = rep(1, n())) %>%
  dplyr::select(distance = value, weights,
         s1.xCoord = lon1, s1.yCoord = lat1, 
         s2.xCoord = lon2, s2.yCoord = lat2, 
         s1.elev = elev1, s1.yday = yday1,
         s2.elev = elev2, s2.yday = yday2) %>%
  data.frame()

@@

### Let's look at per-transect floral survey beta-diversity
```{r}
### 2012
survey_bioData.2012 <- survey %>%
  mutate(year = year(date),
         yday = yday(date)) %>%
  filter(flower.cover > 0 & year == "2012") %>%
  mutate(plant.sp = str_replace_all(plant.sp, " ", "_")) %>%
  group_by(site, yday, plant.sp) %>%
  summarize(cover = sum(flower.cover)) %>%
  mutate(cover = rep(1, n())) %>% # this makes the data binary, which I think is what I want here; otherwise, just comment out
  spread(plant.sp, cover) %>%
  replace(is.na(.), 0) %>%
  arrange(site, yday) %>%
  unite(site.day, site, yday, sep = "_")

@@

survey_sitepair.2012 <- formatsitepair(survey_bioData.2012, bioFormat = 1, siteColumn = "site.day", dist = "jaccard",
                              XColumn = "lon", YColumn = "lat", predData = survey_predData.2012, abundance = FALSE)

@@

### 2011
survey_bioData.2011 <- survey %>%
  mutate(year = year(date),
         yday = yday(date)) %>%
  filter(flower.cover > 0 & year == "2011") %>%
  mutate(plant.sp = str_replace_all(plant.sp, " ", "_")) %>%
  group_by(site, yday, plant.sp) %>%
  summarize(cover = sum(flower.cover)) %>%
  mutate(cover = rep(1, n())) %>% # this makes the data binary, which I think is what I want here; otherwise, just comment out
  spread(plant.sp, cover) %>%
  replace(is.na(.), 0) %>%
  arrange(site, yday) %>%
  unite(site.day, site, yday, sep = "_")

survey_predData.2011 <- survey %>%
  mutate(year = year(date),
         yday = yday(date)) %>%
  filter(flower.cover > 0 & year == "2011") %>%
  select(site, yday) %>%
  left_join(site_data) %>%
  ungroup() %>%
  dplyr::select(site, elev.mean, lat, lon, yday) %>%
  unique() %>%
  arrange(site, yday) %>%
  unite(site.day, site, yday, sep = "_", remove = "FALSE") %>%
  select(-site)

survey_sitepair.2011 <- formatsitepair(survey_bioData.2011, bioFormat = 1, siteColumn = "site.day", dist = "jaccard",
                              XColumn = "lon", YColumn = "lat", predData = survey_predData.2011)

@@

### 2010
survey_bioData.2010 <- survey %>%
  mutate(year = year(date),
         yday = yday(date)) %>%
  filter(flower.cover > 0 & year == "2010") %>%
  mutate(plant.sp = str_replace_all(plant.sp, " ", "_")) %>%
  group_by(site, yday, plant.sp) %>%
  summarize(cover = sum(flower.cover)) %>%
  mutate(cover = rep(1, n())) %>% # this makes the data binary, which I think is what I want here; otherwise, just comment out
  spread(plant.sp, cover) %>%
  replace(is.na(.), 0) %>%
  arrange(site, yday) %>%
  unite(site.day, site, yday, sep = "_")

@@

summary(gdm_bb.2012)
plot(gdm_bb.2012)
plotUncertainty(bb_sitepair.2012, sampleSites = 0.7, bsIters = 50, geo  = TRUE)

                                                 Drosophila?
```
